---
title: "Real Estate Draft"
output: html_document
---

### Setup

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(ggplot2)
```

### Cleaning the Data

```{r}
onalaskaRE = read_csv("Onalaska.csv")
names(onalaskaRE)
```

Variables that we want to get rid of: 
- grantorname
- grantorrelationship
- grantortype
- grantorownintothrnote
- grantorretainsright
- grantorrightsothrnote
- blank...9
- granteename
- granteetype
- granteeaddress
- blank...14
- pageimage
- volumejacket
- blank...19
- county
- physicalpropaddress
- sectw..
- blank...27
- asof
- comments
- officialparcelnumbers
- blank...31
- blank...38
- sendtaxbillto
- name
- streetaddress
- citystatezip
- blank...43
- transfertype
- transfertypeothrnote
- conveydoctype
- conveyothrnote
- conveyancedate
- blank...50
- mflpfcacres
- blank...58
- grantorsagent
- granteesagent
- preparername
- blank...62
- blank...65
- prevdocnumber
- blank...69

```{r}
onalaskaRE = onalaskaRE %>% select(-c("grantorname", "grantorrelationship", "grantortype", "grantorownintothrnote", "grantorretainsright", "grantorrightsothrnote", "blank...9", "granteename", "granteetype", "granteeaddress", "blank...14", "pageimage", "volumejacket", "blank...19", "county", "physicalpropaddress", "sectwshpbaselinerngemeridian", "blank...27", "asof", "comments", "officialparcelnumbers", "blank...31", "blank...38", "sendtaxbillto", "name", "streetaddress", "citystatezip", "blank...43", "transfertype", "transfertypeothrnote", "conveydoctype", "conveyothrnote", "conveyancedate", "blank...50", "mflpfcacres", "blank...58", "grantorsagent", "granteesagent", "preparername", "blank...62", "blank...65", "prevdocnumber", "blank...69", "subdivcondolotunitblock"))
names(onalaskaRE)
```
